### 2021-10-27 sections/2-info-theory.tex
comment on hierarchical encodings
fix bug in equation
names

The \textbf{Metric Entropy} (Kolmogorov Entropy) of the dataset, denoted by $N_{\epsilon}^{ent}(X)$, is the maximum $n$ such that $\{x_1, \dots, x_n\} \subseteq X$ and $f(x_i, x_j) \geq \epsilon \ \forall \ i \neq j$, i.e. the maximum number of $\epsilon$-separated instances in the dataset.

The \textbf{Internal Covering Number} of the dataset, denoted by $N_{\epsilon}^{int}(X)$, is the minimum $n$ such that $\{x_1, \dots, x_n\} \subset X$ and $\bigcup_{i = 1}^{n} C(c_i, \epsilon) = X$, i.e. the minimum number of $\epsilon$-radius clusters that collectively cover $X$.

@@

The \textbf{Fractal Dimension} (Minkowski Dimension) of a dataset is
\begin{align*}
    d(X) &= \lim_{\epsilon \rightarrow 0} \frac{\log \big( N_{\epsilon}^{int}(X) \big) }{\log \big( \frac{1}{\epsilon} \big)}
\end{align*}
However, if $|X|$ is finite then $d(X) = 0$.

@@

% Wait, can't we encode any cluster at depth d with at most d bits? For a binary tree, arbitrarily choose 0 for left and 1 for right, and a length-d traversal uniquely identifies a cluster at depth d. Not sure if this is a weaker upper bound, but we should mention it. For n flat clusters, lg n bits identifies a unique one; for n leaves, lg n bits identifies a leaf, but an internal cluster at depth d only needs lg d bits.
% Actually I see that you sort of get at this in the "back to shannon entropy" subsection, but maybe it could be explained intuitively as I did above?

>>>>

The \textbf{Metric Entropy} (Kolmogorov Entropy) of the dataset, denoted by $N_{\epsilon}^{ent}(X)$, is the maximum $k$ such that $\{x_1, \dots, x_k\} \subseteq X$ and $f(x_i, x_j) \geq \epsilon \ \forall \ i \neq j$, i.e. the maximum number of $\epsilon$-separated instances in the dataset.

The \textbf{Internal Covering Number} of the dataset, denoted by $N_{\epsilon}^{int}(X)$, is the minimum $k$ such that $\{x_1, \dots, x_k\} \subset X$ and $\bigcup_{i = 1}^{k} B(c_i, \epsilon) = X$, i.e. the minimum number of $\epsilon$-radius clusters that collectively cover $X$.

@@

The \textbf{Fractal Dimension} (Minkowski Dimension) of a dataset is
\begin{align*}
    d(X) &= \lim_{\epsilon \rightarrow 0} \frac{\log \big( N_{\epsilon}^{ent}(X) \big) }{\log \big( \frac{1}{\epsilon} \big)}
\end{align*}
However, if $|X|$ is finite then $d(X) = 0$.

@@

% Noah
% Wait, can't we encode any cluster at depth d with at most d bits? For a binary tree, arbitrarily choose 0 for left and 1 for right, and a length-d traversal uniquely identifies a cluster at depth d. Not sure if this is a weaker upper bound, but we should mention it. For n flat clusters, lg n bits identifies a unique one; for n leaves, lg n bits identifies a leaf, but an internal cluster at depth d only needs lg d bits.
% Actually I see that you sort of get at this in the "back to shannon entropy" subsection, but maybe it could be explained intuitively as I did above?

% Najib
% Such a traversal identifies only which cluster it would be. That traversal does not encode (or compress) the cluster-center. For discussing compression and Shannon entropy, we want to encode/compress cluster-centers using the hierarchical relations from the tree in such a way that the child-center is recoverable from a parent-center and the encoding.
% I see that the term `encode' is overloaded here.
